Implementing DNS in C0

### 2017-11-17 proposal.tex
turn on fullpage; update outline
Updated network interface section for clarity.

By splitting the library into these two parts, we can keep the \Kwd{C} portion of our codebase limited in scope. In particular, we plan to ensure that we never dynamically allocate memory from \Kwd{C} and that any accesses to \Kwd{C0}-allocated memory are done so safely. The former is easily checked for, simply by checking that there are no calls to malloc or similar functions, while the latter can be achieved (but less easily checked) by using a collection of functions for safe memory access provided to libraries by the \Kwd{C0} runtime. As a result of this and the small size of the \Kwd{C} portion of the codebase, we can easily check all of our code for memory safety, ensuring that any memory safety violations occur outside of our project (e.g. in the \Kwd{C} sockets library or in the OS).

>>>>

By splitting the library into these two parts, we can keep the \Kwd{C} portion of our codebase limited in scope. In particular, we plan to ensure that we never dynamically allocate memory from \Kwd{C} and that any accesses to \Kwd{C0}-allocated memory are done so safely. The former is easily checked for, simply by checking that there are no calls to malloc or similar functions, while the latter can be achieved (but less easily checked) by using a collection of functions for safe memory access provided to libraries by the \Kwd{C0} runtime. As a result of this and the small size of the \Kwd{C} portion of the codebase, we can easily check all of the \Kwd{C} code for memory safety. Combining this with \Kwd{C0}'s memory safety, we ensure that any memory safety violations occur outside of our project (e.g. in the \Kwd{C} sockets library or in the OS).
